---
title: "R Notebook"
---


```{r}
library(lme4)
soda = read.csv("Soda_choice_data.csv", header=T)
soda.ms = soda[soda$ProductID!=0,]
soda0 = soda$MarketShare[soda$ProductID==0]
soda0 = matrix(soda0, length(soda0), 11)
soda.ms$logMktShrRatio = log(soda.ms$MarketShare/as.vector(t(soda0)))

```
```{r}
lm2 <-lmer(logMktShrRatio~Brand+Sugar+Caffeine+Promotion+(1|Week),soda.ms)
summary(lm2)
```
B0, B1, B2, B3, B4  are significant.

B0 is the baseline market share ratio of soft drinks of Brand 1 compared to outside product (where customer does NOT buy soft drinks)
B1: Market share ratio of soft drinks would decrease if the drink belongs to Brand 2.
B2: Market share ratio of soft drinks would decrease if the drink belongs to Brand 3.
B3: Higher the sugar level, lower the market share ratio of soft drinks
B4: If there is caffeine, the market share ratio of soft drinks will increase
B5: Greater the promotion discount, higher the market share ratio of soft drinks











